---
title: "2022 Monthly Reports"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

Last compiled: `r Sys.Date()`

# January 2022

## Website Updates & Others

* [Black Culture Center Library website](https://www.depts.ttu.edu/library/bcclibrary/) started off
* Requested UX tests for the pages [Personal Librarians](https://www.depts.ttu.edu/library/research-support/personalLibrarians/) and [Software List](https://apps.lib.ttu.edu/services/technology/softOU.php) - reviewed and discussed the test plan
* Maintained [job posts](https://www.depts.ttu.edu/library/about/employment/), [staff directory](https://www.depts.ttu.edu/library/about/staff/index.php), and [org charts](https://www.depts.ttu.edu/library/about/admin/org_chart/org_charts.php)
* Updated the [Open Access Award Recipients](https://www.depts.ttu.edu/library/grants/open-access-award/recipients.php) page
* Helped styling of the chat widget on the [OneSearch](https://ttu-primo.hosted.exlibrisgroup.com/primo-explore/search?institution=01TTU&vid=01TTU&tab=default_tab&search_scope=01TTU_ALL&mode=Basic&displayMode=full&bulkSize=38&highlight=true&dum=true&query=any,contains,&displayField=all) page
* Updated links to the [Development Leave forms](https://www.depts.ttu.edu/library/libstaff/)
* Updated [Arch Library floor plans](https://www.depts.ttu.edu/library/about/facility/maps/arch.php)
* Fixed some broken links
* Confirm the renewal of ESI Application Registrations
* Responded to the UX report on the Personal Librarian's page

## Meetings / Workshops / Training Attended
* Software Carpentry II: Programming with Python by Virginia Tech Libraries
* Software Carpentry II: Programming with R and RStudio by Virginia Tech Libraries
* Library Faculty Meeting
* TX-CARP Monthly Meeting - information collection, 4 possible carpentry workshops
* Unit Meeting


## Research
* Reviewed the data for the book chapter on OA publishing
* Final revision of the paper "Applications, Issues and Reflection on Altmetrics" per editor's request

## Service
* FSC regular meetings, reference check, and phone interviews
* Code4Lib Conf Program Committee meetings - review and schedule programs
* CFSA Events (New Year Celebration) preparation and [website](https://www.depts.ttu.edu/cfsa/) updates 
* IFLA SE section monthly meeting - [section website](https://www.ifla.org/units/statistics-and-evaluation/) updates and programs for the upcoming WLIC 2022
* CALA membership database maintenance

## Others
* R workshops preparation, rehearsals, and deliveries (updated [LibGuides](https://guides.library.ttu.edu/R4Beginners))
* Annual Review
* Triaged and responded emails to the website - 15 queries




```{r}
samples <- rnorm(100, mean=0, sd=1)
hist(samples)
```

When you knit this R Markdown document, you will see that the histogram is printed to the page, along with the R code. This document can be set up to hide the R code in the webpage, just delete the comment (hashtag), from the cold folding option in the yaml header up top. For purposes of letting yourself see the code, and me see the code, best to keep it the way that it is. You learn all of these things and more can be customized in each R code block.




